RDF Validation Requirements - Evaluation and Logical Underpinning

### 2014-12-27 paper/RDF validation requirements/RDF validation requirements.tex
Some editing all over has been done

\begin{center}
\begin{DL} 
$(\forall R.C)^\mathcal{I}= \{a \in \Delta^\mathcal{I}\mid (a,b) \in R^\mathcal{I} \rightarrow b \in C^\mathcal{I} \}$ where $\cdot^\mathcal{I}$ is an interpretation function, \\
$\Delta^I$ is the domain, $a,b \in \Delta^\mathcal{I}$ are individuals $C$ is a concept, $R$ is a role. 
\end{DL}
\end{center}

>>>>

\begin{center}
\begin{DL} 
$(\forall R.C)^\mathcal{I}= \{a \in \Delta^\mathcal{I}\mid (a,b) \in R^\mathcal{I} \rightarrow b \in C^\mathcal{I} \}$ where $\cdot^\mathcal{I}$ is an interpretation function, \\
$\Delta^\mathcal{I}$ is the domain, $a,b \in \Delta^\mathcal{I}$ are individuals $C$ is a concept, $R$ is a role. 
\end{DL}
\end{center}
